|

### 2020-09-14 paper.Rmd
remove old text
add magick

- use four panel set up for grand tour and sage

@@

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\gamma=3$ (bottom)", fig.width="0.9\\textwidth"}
library(cowplot)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_panel <- function(png) ggdraw() + 
  draw_image(png) + 
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))

>>>>

@@

```{r mouse-cluster, fig.cap = "Selected frames from using a tour of the mouse data with the default tour display (top), and the sage display with $\gamma=3$ (bottom)", fig.width="0.9\\textwidth"}
library(cowplot)
library(magick)
dir <- "pngs/"
frames <- c("001", "016", "038", "074")
draw_panel <- function(png) ggdraw() + 
  draw_image(png) + 
  theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
